Classifier Explanation

### 2019-05-02 Paper/paper.Rmd
I included a few edits to my own phrasing and explanation of the model. I also included  a few more visualizations and code chunks that helped explain the model's performance and accuracy.

---
title: "Classifier"
output: github_document
---
# The Classification Model
A key component to successfuly using twitter data to assess service failures is the ability to classify tweets as complaints and non-complaints. If our team can accurately classify a tweet, we will be capable of tackling the greater issue of judging how serious the complaint is, and whether or not a company needs to take action.

While there are a massive number of methods to perform this task, our team has identified three tools to aid us in our classification: Principal Component Analysis (PCA), FastText, and XGBoost. Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above. The model has been trained on 2,500 tweets labeled 0 for "non-complaint" and 1 for "complaint." We have then tested the model on a similarly-sized dataset.

To use our model, we fed a set of tweets into a PCA model and a FastText classification model. The output of these two models is then fed into our XGBoost model, which makes a binary prediction for the tweet as a complaint or non-complaint. I believe that the idea behind this "frankenstein model" is to use the perspectives of various styles of models to gain an accurate consensus on the data -- somewhat similar to the concept behind random forests.

@@

# The FastText Sub-Model
## Overview
In this section, we'll document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

@@

!!!!!! Considering that this is such a large dataset, it might be worthwhile to use -loss hs (hierarchical softmax) to speed up the training. It should not significantly affect accuracy.

@@

### Analysis of Principal Components
Once we had a list-column of average tweet vectors (avg_vec_50), we analyzed its principal components. We started with a 3D visualization of the first three principal components, coloring the tweets by their complaint/non-complaint labels, and found that the complaints and non-complaints grouped well. We also looked at a scree plot and found that four principal components would be effective enough to describe the variance in our data well.

@@

>>>>

---
title: "Classifier Explanation"
output: github_document
---
```{r include = FALSE}
library(tidyverse)
library(caret)
library(xgboost)
library(Matrix)

train <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv"))
```
# The Classification Model
A key component to successfuly using twitter data to assess service failures is the ability to classify tweets as complaints and non-complaints. If our team can accurately classify a tweet, we will be capable of tackling the greater issue of judging how serious the complaint is, and whether or not a company needs to take action.

While many methods available can aid us in this task, our team has identified three tools to help us perform our classification: Principal Component Analysis (PCA), fastText, and XGBoost. Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above. The model has been tested and trained on `r nrow(train) # the number of tweets in our training dataset` tweets labeled 0 for "non-complaint" and 1 for "complaint." We partitioned the data so that about 80% was used for training, and 20% for testing.

To use our model, we fed a set of tweets into a PCA model. The output of the PCA model (unsupervised) was then fed into an XGBoost model (supervised). Simultaneously, we fed the same set of tweets into a fastText classification model (supervised). The frankenstien model then compares predictions of the XGBoost and fastText models, and makes a final prediction. I believe that the idea behind this "frankenstein model" is to use the perspectives of various styles of models to gain an accurate consensus on the data -- somewhat similar to the concept behind random forests.

@@

# The fastText Sub-Model
## Overview
In this section, we will document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

@@

@@

### Analysis of Principal Components
Once we had a list-column of average tweet vectors (avg_vec_50), we analyzed its principal components. We started with a 3D visualization of the first three principal components, coloring the tweets by their complaint/non-complaint labels, and found that the complaints and non-complaints grouped well.

![3D visualization of first three principal components.](../Figures/3D_PCA.png)

We also looked at a scree plot and found that four principal components would be effective enough to describe the variance in our data well.

![Scree plot.](../Figures/screeplot.png)

@@

```{r include = FALSE}
source(here::here("Code", "dallin_annotations", "06_define_prediction_functions.R"))

load(here::here("Output", "train_data.dat"))

trainIndex <- createDataPartition(train$complaint_label, p = .8, 
                                  list = FALSE, 
                                  times = 1)

test_data <- train[-trainIndex,]
test_labels <- test_data %>% select(complaint_label) %>% transmute(label = complaint_label)
test_data_vec <- test_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)

train_data <- train[trainIndex,]
train_labels <- train_data %>% select(complaint_label) %>% transmute(label = complaint_label)
train_data_vec <- train_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)

dtest1 <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec))

bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
               eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)

test_data$prediction <- predict(bst, dtest1)

predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))

test_data <- test_data %>%
  mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
                                   TRUE ~ "Non-complaint"),
         complaint_label = case_when(complaint_label == 1 ~ "Complaint",
                                   TRUE ~ "Non-complaint")) %>%

    mutate(accuracy = predict_label == complaint_label)
```

Confusion matrix output:
```{r}
confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))
```
